\Large \bf Conjure: Summoning Proxies from Unused Address Space

### 2019-05-07 paper/related.tex

\scheme allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the phantom host will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to \scheme.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

>>>>

\scheme allows a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the phantom host will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to \scheme.

@@

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. \scheme furthers this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
